\documentclass{article}
\usepackage{amsmath,amsthm,latexsym}

\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newtheorem*{solution}{Solution}
\newtheorem*{resources}{Resources}

\newcommand{\name}[1]{\noindent\textbf{Name: #1}}
\newcommand{\honor}{\noindent On my honor, as an Aggie, I have neither
  given nor received any unauthorized aid on any portion of the
  academic work included in this assignment. Furthermore, I have
  disclosed all resources (people, books, web sites, etc.) that have
  been used to prepare this homework. \\[2ex]
 \textbf{Signature:} \underline{\hspace*{7cm}} }

 
\newcommand{\checklist}{\noindent\textbf{Checklist:}
\begin{enumerate}
\item[$(~)$] Did you add your name?
\item[$(~)$] Did you disclose all resources that you have used? \\
(This includes all people, books, websites, etc.\ that you have consulted)
\item[$(~)$] Did you sign that you followed the Aggie honor code? 
\item[$(~)$] Did you solve all problems? 
\item[$(~)$] Did you submit (a) your LaTeX source file and (b) the resulting PDF file
  of your homework on eCampus?
\item[$(~)$] Did you submit (c) a signed hardcopy of the PDF file in class? 
\end{enumerate}
}

\newcommand{\problemset}[1]{\begin{center}\textbf{Problem Set #1}\end{center}}
\newcommand{\duedate}[2]{\begin{quote}\textbf{Due dates:} Electronic
    submission of the PDF file for this homework is due on
    \textbf{#1} on \texttt{http://ecampus.tamu.edu}.  A signed paper copy of the PDF is due on
    \textbf{#2} at the beginning of class.\end{quote} }


\begin{document}
\begin{center}
{\large
CSCE 222 [503] Discrete Structures for Computing\\[.5ex]
Spring 2015 -- Philip C. Ritchey\\}
\end{center}

\problemset{2}

\duedate{2/05/2015 (Thursday) before 11:59 p.m.}{2/06/2015 (Friday)}

\name{ (Han Hong) }

\begin{resources} Discrete Mathematics and Its Applications by Rosen, (additional people, books, articles, web pages, etc.\ that
  have been consulted when producing this homework)
\end{resources}

\honor

\bigskip

\begin{problem} (10 points)
Section 1.6, Exercise 4, page 78
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (10 points)
Section 1.6, Exercise 8, page 78
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (10 points)
Section 1.6, Exercise 14 (c) and (d), page 79
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (10 points)
Section 1.6, Exercise 18, page 79
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (10 points)
Section 1.6, Exercise 34, page 80
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (10 points)
Section 1.7, Exercise 18, page 91
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (10 points)
Section 1.7, Exercise 24, page 91
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (10 points)
Section 1.7, Exercise 38, page 92
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (10 points)
Section 1.8, Exercise 28, page 108
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (10 points)
Section 1.8, Exercise 34, page 109
\end{problem}
\begin{solution}
\end{solution}

\goodbreak
\checklist
\end{document}
